Reducing RES Droughts through the integration of wind and PV

### 2025-01-15 Article2/elsarticle-template-harv.tex
Update highlights

\author[Math]{Aina Maimo Far} %% Author name
\ead{aina.maimofar@ucd.ie}

@@

\item Two C3S-Energy and one custom models are compared to assess RES droughts in Ireland

\item RES drought trends are explored by analysing 45 years of ERA5 weather data

\item Diverse energy mix reduces RES drought frequency, duration and extremes

\item Model selection is crucial in the accurate identification of RES droughts

>>>>

\author[Math]{Aina Maimó Far} %% Author name
\ead{aina.maimofar@ucd.ie}

@@

\item RES droughts are analysed using 45 years of hourly wind and PV generation data

\item RES droughts from C3S-Energy and ERA5-Atlite datasets are compared

\item Adding PV to a wind-dominated system reduces RES drought frequency and duration

\item Validated RES datasets are crucial to accurately identify RES drought extremes
